---
title: "NormsSharingPilot2"
output:
  pdf_document: default
  html_document: default
date: "2023-03-22"
---

# Load packages

```{r}

install.packages("broom.mixed")
```

```{r}
library(broom.mixed)
library(modelsummary)
library(tidyr)
library(car)
library(dplyr)
library(xtable)
library(reshape2)
library(lme4)
library(emmeans)
library(dplyr)
library(plm)
library(sandwich)
library(stringr)
library(jtools)
library(readr)
library(stargazer)
library(lubridate)
library(ggthemes)
library(vtable)
library(lme4)
library(ggplot2)
library(ggtext)
library(lmerTest)
library(stargazer)
library(texreg)
```

# Process data

## look at demo freq

```{r}
df <- read.csv("may18.csv")
df <- df[!is.na(df$IPAddress) & df$IPAddress != "", ]
#View(df)
```

```{r}
dfd <- df

# colum names 
gender.cols <- c(
  "gender.woman",
  "gender.man",
  "gender.nb",
  "gender.notdis"
)

# initalize new 
dfd[, gender.cols] <- 0

dfd$gender.woman <- as.numeric(grepl("1",dfd$Gender))
dfd$gender.man <- as.numeric(grepl("2",dfd$Gender))
dfd$gender.nb <- as.numeric(grepl("3",dfd$Gender))
dfd$gender.notdis <- as.numeric(grepl("4",dfd$Gender))

table(dfd$gender.woman)
table(dfd$gender.man)
table(dfd$gender.nb)
table(dfd$gender.notdis)
```

```{r}
# colum names 
lg.cols <- c(
  "lg.str",
  "lg.gay",
  "lg.les",
  "lg.bi",
  "lg.pan",
  "lg.qu",
  "lg.ase",
  "lg.notdis",
  "lg.self"
)

# initalize new 
dfd[, lg.cols] <- 0

dfd$lg.str <- as.numeric(grepl("1",dfd$LGBTQ))
dfd$lg.gay <- as.numeric(grepl("2",dfd$LGBTQ))
dfd$lg.les <- as.numeric(grepl("3",dfd$LGBTQ))
dfd$lg.bi <- as.numeric(grepl("4",dfd$LGBTQ))
dfd$lg.pan <- as.numeric(grepl("5",dfd$LGBTQ))
dfd$lg.qu <- as.numeric(grepl("6",dfd$LGBTQ))
dfd$lg.ase <- as.numeric(grepl("7",dfd$LGBTQ))
dfd$lg.notdis <- as.numeric(grepl("8",dfd$LGBTQ))
dfd$lg.self <- as.numeric(grepl("9",dfd$LGBTQ))


table(dfd$lg.str)
table(dfd$lg.gay)
table(dfd$lg.les)
table(dfd$lg.bi)
table(dfd$lg.pan)
table(dfd$lg.ase)
table(dfd$lg.notdis)
table(dfd$lg.self)
```

```{r}
race.cols <- c(
  "race.white",
  "race.lat",
  "race.afr",
  "race.asian",
  "race.ind",
  "race.isl",
  "race.mid",
  "race.other"
)

# initalize new 
dfd[, race.cols] <- 0

dfd$race.white <- as.numeric(grepl("1",dfd$Race))
dfd$race.lat <- as.numeric(grepl("2",dfd$Race))
dfd$race.afr <- as.numeric(grepl("3",dfd$Race))
dfd$race.asian <- as.numeric(grepl("4",dfd$Race))
dfd$race.ind <- as.numeric(grepl("5",dfd$Race))
dfd$race.isl <- as.numeric(grepl("6",dfd$Race))
dfd$race.mid <- as.numeric(grepl("7",dfd$Race))
dfd$race.other <- as.numeric(grepl("8",dfd$Race))

table(dfd$race.white)
table(dfd$race.lat)
table(dfd$race.afr)
table(dfd$race.asian)
table(dfd$race.ind)
table(dfd$race.isl)
table(dfd$race.mid)
table(dfd$race.other)

```

## main processing

```{r}

df <- df[-c(1,2),] # remove extra rows

demo.cols <- c("Race", "Gender", "LGBTQ", "Age", "Parental.status", "Religion")

# this is the X5_sms...
factor.cols <- grep("X\\d*_\\w*.\\w*", colnames(df), value = TRUE)

melted_df <- melt(df, id.vars = c("ResponseId", demo.cols),
                  measure.vars = factor.cols,
                  variable.name = "factor_demo",
                  value.name = "rating")

# remove empty ratings
melted_df <- melted_df[!is.na(melted_df$rating) & melted_df$rating != "",]

melted_df$factor_demo <- as.character(melted_df$factor_demo)

get_location <- function(g) {
  number <- as.numeric(substring(strsplit(g, "_")[[1]], 2)[1])
  
  if (number %in% c(1, 2, 3)) {
    return("gym")
  } else if (number %in% c(4, 5, 6)) {
    return("home")
  } else if (number %in% c(7, 8, 9)) {
    return("street")
  } else if (number %in% c(10, 11, 12)) {
    return("coffee")
  } else if (number %in% c(13, 14, 15)) {
    return("control")
  } else {
    return(NA)
  }
}

# CURRENT ISSUE: WHAT IS X16? CURRENTLY IT IS NA 
melted_df$location <- apply(melted_df, 1, function(row) get_location(row["factor_demo"]))


get_relationship <- function(g) {
  number <- as.numeric(substring(strsplit(g, "_")[[1]], 2)[1])
  
  if (number %in% c(1, 4, 7, 10, 13)) {
    return("closefriend")
  } else if (number %in% c(2, 5, 8, 11, 14)) {
    return("acquaintance")
  } else if (number %in% c(3, 6, 9, 12, 15)) {
    return("dontknow")
  } else {
    return(NA)
  }
}

melted_df$relationship <- apply(melted_df, 1, function(row) get_relationship(row["factor_demo"]))

# make another column to clean factor_demo
melted_df$`platformaudience` <- sub("^[^_]*_", "", melted_df$factor_demo)

#change all rating to as.numeric 
melted_df$rating <- as.numeric(melted_df$rating)

# some lack all demo, remove those. ASK CAMI 
melted_df <- melted_df[!is.na(melted_df$Age) & melted_df$Age !="",]

df<-melted_df

df<- na.omit(df) # REMOVE ALL NA FROM THE X16s

View(df)

```

-   NOTES

-   all X16 are NA

-   all NA's are removed

-   some lack ALL demos, and are removed

# Means calc

```{r}
# by platform 
plt.names <- unique(df$platformaudience)

for(plt in plt.names){
  m <- mean(df$rating[df$platformaudience == plt])
  #print(paste(plt,m))
}


# by location
mean(df$rating[df$location == "home"])
mean(df$rating[df$location == "gym"])
mean(df$rating[df$location == "street"])
mean(df$rating[df$location == "coffee"])
mean(df$rating[df$location == "control"])



# by relationship
mean(df$rating[df$relationship == "closefriend"])
mean(df$rating[df$relationship == "acquaintance"])
mean(df$rating[df$relationship == "dontknow"])


# interactions, 2 way or 3 way
mean(df$rating[df$relationship == "closefriend" & 
     df$platformaudience == "facebook.groupchat"])

mean(df$rating[df$relationship == "dontknow" & 
     df$platformaudience == "tiktok.video"])

mean(df$rating[df$relationship == "closefriend" & 
     df$platformaudience == "sms.groupchat" &
     df$location == "home"])
```

# Demographics Data Processing (1,0)

## gender

```{r}

#table(df$Gender)

# colum names 
gender.cols <- c(
  "gender.woman",
  "gender.man",
  "gender.nb"
)

# initalize new 
df[, gender.cols] <- 0

df$gender.woman <- as.numeric(grepl("1",df$Gender))
df$gender.man <- as.numeric(grepl("2",df$Gender))
df$gender.nb <- as.numeric(grepl("3",df$Gender))
#df$gender.notdis <- as.numeric(grepl("4",df$Gender))

```

## lgbtq

```{r}

#table(df$LGBTQ)

# colum names 
lg.cols <- c(
  "lg.str"
)

# initalize new 
df[, lg.cols] <- 0

df$lg.str <- as.numeric(grepl("1",df$LGBTQ))
#df$lg.queer <- as.numeric(grepl("2|3|4|5|6|7|8|9",df$LGBTQ))

#df$lg.str <- as.numeric(grepl("1",df$LGBTQ))
#df$lg.gay <- as.numeric(grepl("2",df$LGBTQ))
#df$lg.les <- as.numeric(grepl("3",df$LGBTQ))
#df$lg.bi <- as.numeric(grepl("4",df$LGBTQ))
#df$lg.pan <- as.numeric(grepl("5",df$LGBTQ))
#df$lg.qu <- as.numeric(grepl("6",df$LGBTQ))
#df$lg.ase <- as.numeric(grepl("7",df$LGBTQ))
#df$lg.notdis <- as.numeric(grepl("8",df$LGBTQ))
#df$lg.self <- as.numeric(grepl("9",df$LGBTQ))

#View(df)

```

## race

```{r}
#table(df$Race)

# colum names 
race.cols <- c(
  "race.white.mid.ind",
  "race.lat",
  "race.afr",
  "race.asian.isl"
)

# initalize new 
df[, race.cols] <- 0

df$race.white.mid.ind <- as.numeric(grepl("1|7|5",df$Race))
df$race.lat <- as.numeric(grepl("2",df$Race))
df$race.afr <- as.numeric(grepl("3",df$Race))
df$race.asian.isl <- as.numeric(grepl("4|6",df$Race))

#View(df)

```

## parental

```{r}
#table(df$Parental.status)

parent.cols <- c(
  "parent.yes"
)

df[,parent.cols] <- 0
df$parent.yes <- as.numeric(grepl("2|3|4|5",df$Parental.status))
#df$parent.no <- as.numeric(grepl("1",df$Parental.status))
#df$parent.notdis <- as.numeric(grepl("6",df$Parental.status))

#View(df)
```

## religion

```{r}

# More than 10, grepl gets confused
table(df$Religion)

# make into num to count 
df$Religion <- as.numeric(df$Religion)

relig.cols <- c(
  "relig.yes"
)

df[,relig.cols] <- 0

df$relig.yes <- as.numeric(df$Religion %in% c(1,2,3,4,5,6,7,8,9,12))
#df$relig.no <- as.numeric(df$Religion %in% c(10,11))
#df$relig.notdis <- as.numeric(df$Religion %in% c(13))

#View(df)
```

# Model selection

## enumerate models 

```{r}
mod.str <- c(
  "platformaudience + relationship + location + (1|ResponseId)",
  "platformaudience*relationship + location + (1|ResponseId)",
  "platformaudience*location + relationship  + (1|ResponseId)",
  "platformaudience + location*relationship  + (1|ResponseId)",
  "platformaudience*location*relationship  + (1|ResponseId)"
)

#no demo models 
mod.main <- lmer(rating ~ platformaudience + relationship + location + (1|ResponseId), data=df)
mod.pr_l <- lmer(rating ~ platformaudience*relationship + location + (1|ResponseId), data=df)
mod.pl_r <- lmer(rating ~ platformaudience*location + relationship  + (1|ResponseId), data=df)
mod.lr_p <- lmer(rating ~ platformaudience + location*relationship  + (1|ResponseId), data=df)
mod.lrp <- lmer(rating ~ platformaudience*location*relationship  + (1|ResponseId), data=df)

# add demographics to each 
all.demo.features <- c(gender.cols, race.cols, lg.cols, relig.cols, parent.cols)

#demo models
tmp.formula <- as.formula(paste("rating ~ ", paste(mod.str[[1]], "+" , paste(all.demo.features, collapse="+"))))
mod.main.d <- lmer(tmp.formula, data=df)
tmp.formula <- as.formula(paste("rating ~ ", paste(mod.str[[2]], "+" , paste(all.demo.features, collapse="+"))))
mod.pr_l.d <- lmer(tmp.formula, data=df)
tmp.formula <- as.formula(paste("rating ~ ", paste(mod.str[[3]], "+" , paste(all.demo.features, collapse="+"))))
mod.pl_r.d <- lmer(tmp.formula, data=df)
tmp.formula <- as.formula(paste("rating ~ ", paste(mod.str[[4]], "+" , paste(all.demo.features, collapse="+"))))
mod.lr_p.d <- lmer(tmp.formula, data=df)
tmp.formula <- as.formula(paste("rating ~ ", paste(mod.str[[5]], "+" , paste(all.demo.features, collapse="+"))))
mod.lrp.d <- lmer(tmp.formula, data=df)



```

## DEPRECATED: find min AIC model

```{r}
# Calculate the AIC of each model
aic.main <- AIC(mod.main)
aic.pr_l <- AIC(mod.pr_l)
aic.pl_r <- AIC(mod.pl_r)
aic.lr_p <- AIC(mod.lr_p)
aic.lrp <- AIC(mod.lrp)
aic.main.d <- AIC(mod.main.d)
aic.pr_l.d <- AIC(mod.pr_l.d)
aic.pl_r.d <- AIC(mod.pl_r.d)
aic.lr_p.d <- AIC(mod.lr_p.d)
aic.lrp.d <- AIC(mod.lrp.d)

all.aic <- c(
  aic.main,aic.pr_l,aic.pl_r,aic.lr_p,aic.lrp,
  aic.main.d,aic.pr_l.d,aic.pl_r.d,aic.lr_p.d,aic.lrp.d
)

# plot in chart 
aic_df <- data.frame(
  Interactions = c(
    "None", "PlatformAudience x Relationship", "PlatformAudience x Location", "Location x Relationship", "Location x Relationship x PlatformAudience","None demo", "PlatformAudience x Relationship demo", "PlatformAudience x Location demo", "Location x Relationship demo", "Location x Relationship x PlatformAudience demo"
    ),
  AIC = all.aic
)
aic_df <- aic_df[order(aic_df$AIC), ]
tbl <- xtable(aic_df, caption="AIC of Different Model Interactions")
View(aic_df)
#tbl
# plot best table

min_aic_index <- which.min(aic_df$AIC)
model_list <- list(
  mod.main, mod.pr_l, mod.pl_r, mod.lr_p, mod.lrp,
  mod.main.d, mod.pr_l.d, mod.pl_r.d, mod.lr_p.d, mod.lrp.d)
mod <- model_list[[min_aic_index]]

#stargazer(mod, type='latex', caption="Model predicting sharing appropiateness")
```

## RQ0. anova all models 

```{r}
#f test 
anova.res <- anova(
  mod.main, mod.pr_l, mod.pl_r, mod.lr_p, mod.lrp,
  mod.main.d, mod.pr_l.d, mod.pl_r.d, mod.lr_p.d, mod.lrp.d
)
#stargazer(anova.res, title = "ANOVA Results", type = "latex")
anova.df <- as.data.frame(anova.res)
anova.df <- anova.df[order(anova.df$AIC),]
#View(anova.df)
```

## ANOVA TABLE

```{r}
tbl <- xtable(anova.df, caption="AIC, BIC, and log likelihood of Different Model Interactions")
tbl
```

## MODEL TABLE 

```{r}
mod <- mod.pr_l.d
mod.df <- modelplot(mod, draw=FALSE)
mod.df <- subset(mod.df, select= c(term, estimate, p.value))
#View(mod.df)

# make coef table with bolded significant terms
mod.df.table <- mod.df
mod.df.table$term <- ifelse(mod.df.table$p.value < 0.05, paste0("\\textbf{", as.character(mod.df.table$term), "}"), as.character(mod.df.table$term))

#View(mod.df.table)

xtable(mod.df.table)
```

## MODEL FIGURE plot best model coefs

```{r}
res <- broom.mixed::tidy(mod, effects = "fixed", conf.int = TRUE)
res <- res[, c("term", "estimate", "std.error", "conf.low", "conf.high")]
ggplot(res, aes(x = estimate, y = reorder(term, estimate))) +
  geom_point() +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high)) +
  theme_minimal() +
  xlab("Estimate") +
  ylab("Variable") +
  ggtitle("Confidence Intervals for Model Estimates")

res
ggsave("plot.png", height = 8, width = 6)
```

# Set up figures

```{r}

# platform and audience in new separate cols 

df$platform <- sapply(strsplit(as.character(df$platformaudience), "\\."), `[`, 1)
df$audience <- sapply(strsplit(as.character(df$platformaudience), "\\."), `[`, 2)
#View(df)

# Let's look at means
plat_ems <- emmeans(mod, ~platformaudience)
em_df <- as.data.frame(plat_ems)
View(em_df)
```

```{r}
# Now let's look at pairwise comparisons
pairs(plat_ems, p.adjust='fdr')
```

# Figures

```{r prepare data}

library(ggstance)

overall_mean <- mean(df$rating)
ems <- emmeans(mod, ~ platformaudience)
ems_df <- as.data.frame(ems)
ems_df <- ems_df %>% arrange(desc(emmean))
ems_df$scaled_mean <- ems_df$emmean - overall_mean
ems_df$id <- paste(ems_df$platform, ems_df$audience, sep = ":")
ems_df$id <- ems_df$id <- substring(ems_df$id, 1, nchar(ems_df$id) - 1)

ems_df <- ems_df %>%
  separate(platformaudience, into = c("platform", "audience"), sep = "\\.")

ems_df$lower.CL <- ems_df$asymp.LCL
ems_df$upper.CL <- ems_df$asymp.UCL

View(ems_df)
```

## RQ1.platformaudience 

```{r working}
gg <-
  ggplot(data = ems_df, aes(y = reorder(id, scaled_mean), x = scaled_mean)) +
  geom_point(aes(color = scaled_mean), size = 4) +
  geom_linerange(
    aes(
      xmin = lower.CL - overall_mean,
      xmax = upper.CL - overall_mean,
      y = reorder(id, scaled_mean)
    ),
    color = "grey50",
    size = 0.5
  ) +
  scale_color_gradient2(
    low = "red",
    mid = "gray",
    high = "darkgreen",
    midpoint = 0,
    guide = 'none'
  ) +
  geom_vline(xintercept = 0,
             linetype = "dashed",
             color = "black") +
  theme_nice() + 
  labs(title = "Mean Appropiateness Ratings by Platform and Audience",subtitle="Point estimates and 95% CIs from mixed model",
       x = "(Platform + Audience Mean) - (Overall Mean)", y="Platform + Audience")

gg

ggsave("RQ1platformaudience.png", dpi=300, width = 10, height = 6, units = "in")

```

## DEPRECATED

```{r colored_y_working}
# Extract the unique platforms from the data
library(RColorBrewer)

unique_platforms <- unique(ems_df$platform)
num_platforms <- length(unique_platforms)

# Generate a color palette based on the number of unique platforms
# platform_colors <- colorRampPalette(brewer.pal(5, "Set1"))(num_platforms)
# names(platform_colors) <- unique_platforms

platform_colors <-  c(
  "sms"="#aec3b0", 
  "instagram"="#e2adf2", 
   "tiktok"="#ff8c42", 
  "facebook"="#3e517a", 
  "tweet"="#379392", 
  "reddit"="#7b2d26")
  
unique_platforms <- unique(ems_df$platform)
names(platform_colors) <- unique_platforms

# Create a function to assign colors to y-axis labels based on platform
get_platform_color <- function(platform) {
  return(platform_colors[[platform]])
}

# Modify the ggplot code to include colored y-axis labels
gg <-
  ggplot(data = ems_df, aes(y = reorder(id, scaled_mean), x = scaled_mean)) +
  geom_point(aes(color = scaled_mean), size = 4) +
  geom_linerange(
    aes(
      xmin = lower.CL - overall_mean,
      xmax = upper.CL - overall_mean,
      y = reorder(id, scaled_mean)
    ),
    color = platform_colors[platform],
    size = 0.5
  ) +
  scale_color_gradient2(
    low = "red",
    mid = "gray",
    high = "darkgreen",
    midpoint = 0,
    guide = 'none'
  ) +
  scale_y_discrete(labels = function(x) {
    platform <- gsub("^(.+?):.+$", "\\1", x)
    color <- sapply(platform, get_platform_color)
    color <- "black"
    return(stringr::str_wrap(paste0('<span style="color:', color, ';">', x, '</span>')))
  }) +
  geom_vline(xintercept = 0,
             linetype = "dashed",
             color = "black") +
  theme_nice() + 
  labs(title = "Mean Appropiateness Ratings by Platform and Audience",subtitle="Point estimates and 95% CIs from mixed model",
       x = "(Platform + Audience Mean) - (Overall Mean)", y="Platform + Audience") +
  theme(axis.text.y = element_markdown())

#gg
#ggsave("colored_y.png", dpi=300, width = 10, height = 6, units = "in")

```

```{r colored_points}

gg <-
  ggplot(data = ems_df, aes(y = reorder(id, scaled_mean), x = scaled_mean)) +
  geom_point(aes(color = factor(gsub("^(.+?):.+$", "\\1", id))), size = 4) +
  geom_linerange(
    aes(
      xmin = lower.CL - overall_mean,
      xmax = upper.CL - overall_mean,
      y = reorder(id, scaled_mean)
    ),
    color = "grey50",
    size = 0.5
  ) +
  scale_color_manual(values = platform_colors,  name = "Platform") +
  scale_y_discrete(labels = function(x) {
    platform <- gsub("^(.+?):.+$", "\\1", x)
    #color <- sapply(platform, get_platform_color)
    color <- "black"
    return(stringr::str_wrap(paste0('<span style="color:', color, ';">', x, '</span>')))
  }) +
  geom_vline(xintercept = 0,
             linetype = "dashed",
             color = "black") +
  theme_nice() + 
  labs(title = "Mean Appropriateness Ratings by Platform and Audience", subtitle="Point estimates and 95% CIs from mixed model",
       x = "(Platform + Audience Mean) - (Overall Mean)", y="Platform + Audience") +
  theme(axis.text.y = element_markdown())

#gg

#ggsave("colored_y_colored_p.png", dpi=300, width = 10, height = 6, units = "in")





```

```{r colored_points_no_ci}
gg <-
  ggplot(data = ems_df, aes(y = reorder(id, scaled_mean), x = scaled_mean)) +
  geom_point(aes(color = factor(gsub("^(.+?):.+$", "\\1", id))), size = 4) +
  scale_color_manual(values = platform_colors,  name = "Platform") +
  scale_y_discrete(labels = function(x) {
    platform <- gsub("^(.+?):.+$", "\\1", x)
    #color <- sapply(platform, get_platform_color)
    color <- "black"
    return(stringr::str_wrap(paste0('<span style="color:', color, ';">', x, '</span>')))
  }) +
  geom_vline(xintercept = 0,
             linetype = "dashed",
             color = "black") +
  theme_nice() + 
  labs(title = "Mean Appropriateness Ratings by Platform and Audience", subtitle="Point estimates from mixed model",
       x = "(Platform + Audience Mean) - (Overall Mean)", y="Platform + Audience") +
  theme(axis.text.y = element_markdown())

#gg

#ggsave("colored_y_colored_p_no_ci.png", dpi=300, width = 10, height = 6, units = "in")


```

## RQ3. which platformaudience is least appropriate

```{r stacked_bar}
# change bt platform and platform audience 

palette_red_to_green <- colorRampPalette(colors = c("red", "darkgreen"))(5)

df_proportions <- df %>%
  group_by(platformaudience, rating) %>%
  summarize(count = n()) %>%
  mutate(total = sum(count),
         percentage = count / total * 100)

df_proportions <- df_proportions %>%
  group_by(platformaudience) %>%
  mutate(mean_rating = sum(rating * count) / sum(count),
         prop_rating_5 = sum(ifelse(rating == 5, count, 0)) / sum(count)) %>%
  ungroup()

prop <- ggplot(df_proportions, aes(y = reorder(platformaudience, prop_rating_5), x = percentage, fill = as.factor(rating))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(percentage, 1), "%")),
            position = position_stack(vjust = 0.5),
            color='white',
            size = 3) +
  scale_fill_manual(values = palette_red_to_green, name = "Rating") +
  labs(title = "Stacked Bar Chart of Ratings by PlatformAudience",
       x = "Percentage",
       y = "PlatformAudience") +
  theme_nice()

prop
ggsave("RQ3.platformaudience.ratings", dpi=300, width = 10, height = 6, units = "in")

```

## RQ3.platform

```{r}

palette_red_to_green <- colorRampPalette(colors = c("red", "darkgreen"))(5)

df_proportions <- df %>%
  group_by(platform, rating) %>%
  summarize(count = n()) %>%
  mutate(total = sum(count),
         percentage = count / total * 100)

df_proportions <- df_proportions %>%
  group_by(platform) %>%
  mutate(mean_rating = sum(rating * count) / sum(count),
         prop_rating_5 = sum(ifelse(rating == 5, count, 0)) / sum(count)) %>%
  ungroup()

prop <- ggplot(df_proportions, aes(y = reorder(platform, prop_rating_5), x = percentage, fill = as.factor(rating))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(percentage, 1), "%")),
            position = position_stack(vjust = 0.5),
            color='white',
            size = 3) +
  scale_fill_manual(values = palette_red_to_green, name = "Rating") +
  labs(title = "Stacked Bar Chart of Ratings by Platform",
       x = "Percentage",
       y = "Platform") +
  theme_nice()

prop
ggsave("RQ3.platform.ratings", dpi=300, width = 10, height = 6, units = "in")

```
